---
title: "Our World in Data: Key Crop Yields"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Our World in Data: Key Crop Yields}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6.5,
  fig.height = 5
)
```

```{r setup}
library(cwdata)
```

## Loading the data

A dataset containing crop yields for countries over time. Yields are measured in tonnes per hectare for seven crops. The data is contained within a tibble with 143825 observations and 5 variables.

Once the package is loaded the data can be accessed using the following command:
```{r}
library(cwdata)
library(tibble)
key_crop_yields
```

## Exploration of data

A simple visualisation of a countries crop output is a single year can be created using the method below:
```{r plot1}
library(ggplot2)
library(dplyr)

key_crop_yields %>%
  filter(entity == "Australia",
         year == "2018") %>%
  ggplot(aes(x = reorder(crop, -tonnes_per_hectare),
             y = tonnes_per_hectare)) +
  geom_col()
```
Or the change in crop yields over time can be plotted:
```{r plot2}
library(ggplot2)
library(dplyr)

key_crop_yields %>%
  filter(entity == "Australia") %>%
  ggplot(aes(x = year,
             y = tonnes_per_hectare,
             colour = crop)) +
  geom_line() +
  labs(x = "Tonnes per hectare",
       y = "Year") +
  theme_bw()
```

